---
output:
  word_document: default
  html_document: default
---
Levi Moore

850435436

Module 4 Assignment 1

```{r}
options(tidyverse.quiet = TRUE)
library(tidyverse)
library(VIM)
library(mice)
```

```{r}
ClassGrades = read.csv("class-grades.csv")
```

Task 1
```{r}
summary(ClassGrades)
```
Prefix and Assignment both have no missing data.  Tutorial has one missing value, while Midterm and TakeHome both have three each.  The Final variable has four missing values.


Task 2
```{r}
vim_plot = aggr(ClassGrades, numbers = TRUE, prop = c(TRUE, FALSE), cex.axis=.7)
```
There is only one student who has more than one missing variable.  That student is missing a value for the variables midterm and TakeHome.

Task 3
```{r}
RowDel_ClassGrades = ClassGrades %>% drop_na(Tutorial, Midterm, TakeHome, Final)
vim_plot = aggr(RowDel_ClassGrades, numbers = TRUE, prop = c(TRUE, FALSE), cex.axis=.7)

```
After doing row-wise deletion, 89 rows remain.

Task 4
```{r}
ColumnDel_ClassGrades = ClassGrades %>% select(-Tutorial, -Midterm, -TakeHome, -Final)
vim_plot = aggr(ColumnDel_ClassGrades, numbers = TRUE, prop = c(TRUE, FALSE), cex.axis=.7)
```
After doing row-wise deletion, only two columns remain.


Task 5
After comparing the datasets remaining, I would use the data set that was row-wise deleted.  While the column-wise deletion left all 99 observations in tact, you can only analyze the prefix and assignment variables.  I would much rather look at a the row-wise deleted dataset, which still includes all variables and just ten less oberservations. This data set would prove to be more useful when taking into account the midterm, final, takehome, and tutorial assignments if trying to predict a students grade on the final.

Task 6
```{r}
grades_imp = mice(ClassGrades, m=1, method = "pmm", seed = 12345)
#in line above: m=1 -> runs one imputation, seed sets the random number seed to get repeat summary(grades_imp)
densityplot(grades_imp)
#red imputed, blue original, only shows density plots when more than 1 value the variable #note that the density plots are fairly uninteresting given the small amount of missing data 
grades_complete = complete(grades_imp)
summary(grades_complete)
```


Task 7
Poential issues can occur when working with data that is incomplete, and values are missing. If you are missing data and complete the analysis, the numbers can be skewed (could be for good and bad) which could lead to bad decision making.  While imputation can be good in the sense that it "completes" a dataset, it can also be bad.  For instance, if a company is doing a soft launch of a product.  If you are collecting the age of who purchased this product, but the data is incomplete since not all the customers entered their age.  The company may use the data they have to tailor their advertising to a specific age range.  If you imput the data, this could not give a realistic view of what ages actually purchased this product, and thus causing the company to make a bad decision in the age range for their target audience.















