---
output:
  word_document: default
  html_document: default
---
Levi Moore
850435436
Module 2 Assignment 1

```{r}
library(GGally)
library(tidyverse)

```


Task 1
```{r Task 1}
air = airquality
head(air)
```

A. This dataset has figures concerning the ozone, solar, wind, temp, month and day.

B. This dataset has 153 observations and 6 variables.

C. There is mising data in the following variables: 'Ozone' and 'Solar.R'.

D. Ozone is likely the (Y) variable.  This variable is dependent on the other variables listed.



Task 2
```{r Task 2}
air2 = air %>% filter(!is.na(Ozone)) %>% filter(!is.na(Solar.R))
head(air2)
```
The new dataset, air2, contains 111 rows (observations) and 6 columns (variables)



Task 3
```{r Task 3}
ggpairs(air2)
ggcorr(air2, label = TRUE)
```

A. The variable that is most strongly correlated with the 'Ozone' variable is the 'Temp' variable.

B. The variable that is least strongly correlated with the 'Ozone' variable is the 'Day' variable.


Task 4
```{r Task 4}
ggplot(air2, aes(x=Temp, y=Ozone))+
  geom_point()
```
There is a slight, positive relationshio between these two variables.  As the 'temp' increases, the 'ozone' figure increases gradually.

Task 5
```{r}
model1 = lm(formula = Ozone~Temp, data = air2)
summary(model1)
confint(model1)
```

A. The R squared value is relatively, at 0.488.  Since the coefficient is low (2.91) there isn't a large correalation between these two.

B. The slope conefficient will likely fall between 1.96 and 2.91, looking at a 95% confidence interval.

Task 6
```{r}
ggplot(air2, aes(x=Temp, y=Ozone))+
  geom_point()+
geom_smooth(method = "lm", se = FALSE)
```


Task 7
```{r}
#Manual
#-147.65+2.44*80=
#Prediction 47.55

```


Task 8
```{r}
ggplot(air2, aes(x=Day, y=Ozone))+
  geom_point()
```
There is no relationship between the two variables "Day" and "Ozone".  This shows a 0.0 correlation.

Task 9
```{r}
model2=lm(formula = Ozone~Day, data = air2)
summary(model2)
confint(model2)
```

A. The quality of this model is not great.  The correalation itself is is basically 0, the R squared value is larger than that of model1, and the intercept is lower, but the data doesnt lend itself to telling a story of a relationship between"Day" and "Ozone".

B.  The slope coefficient will likely fall between -0.75 and 0.71, in a 95% confidence interval.

Task 10
```{r}
ggplot(air2, aes(x=Day, y=Ozone))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)
```

